基于GlusterFS的数据分布策略研究

### 2018-09-13 FS/background/log.tex
9.13

\documentclass{article}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{xeCJK}
\usepackage{hyperref}
\usepackage{listings}
\lstset{
 columns=fixed,       
 numbers=left,                                        % 在左侧显示行号
 numberstyle=\tiny\color{gray},                       % 设定行号格式
 frame=single,                                          % 不显示背景边框
 keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
 numberstyle=\footnotesize\color{darkgray},           
 commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
 stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
 showstringspaces=false,                              % 不显示字符串中的空格
 language=c++,                                        % 设置语言
}
\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
\newcommand{\book}[2]{\href[page=#2]{./books/#1.pdf}{(P#2)}}

\title{Near-Data Processing}
\author{陈辉}
\date{}
\begin{document}
\maketitle
\tableofcontents
\newpage
\part{文献}
\section{\textit{Cloud-Scale-Acceleration-Architecture}}
\paper{Cloud-Scale-Acceleration-Architecture}{1}
\subsection{Introduction}
\textbf{Balance of Homogeneity and Specialization}\par
Specialized accelerator should be programmable to adjust the diversity of cloud servers and rapid change. That's why we need FPGAs or GPUs.\\

This paper describes a cloud-scale FPGA-based acceleration architecture called \textit{Configurable Cloud} which allows datapath of cloud communication to be accelerated with FPGAs. This datapath can include networking flows, \textbf{storage flows}, security operations and distributed applications.\\

We use a protocol called \textbf{LTL(Lightweight Transport Layer)} to make the remote FPGA resources apper closer than either a single local SSD access or the time to get through the host's networking stack.\\

\subsection{Hardware Architecture}
\textbf{Designing Requirements}
\begin{itemize}
\item Homogeneity.
\item Fungibility.
\item Flexibility.

\begin{itemize}
\item \textit{Local compute acceleration(through PCIe)}.
Local acceleration handles \textbf{hight-value scenarios} such as search rankingon each FPGA's host. 
\item \textit{Network acceleration.} 
e.g. intrusion detection, deep packet inspection and network encryption.
\item \textit{Global application acceleration(through FPGA pools)}. Through this, idle FPGAs can be used for distributed large-scale applications such as machine learning.
\end{itemize}

\item \textbf{Physical restrictions}. e.g. physical space, power consumption, and temperature. That's \textbf{why we choose FPGAs instead of GPUs}.
\end{itemize}

\section{\textit{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}}
See paper\paper{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}{1}
See presentation\paper{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks(Presentation)}{1}

\includepdf[link=true,pages=-,fitpaper]{./papers/Cloud-Scale-Acceleration-Architecture.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks.pdf}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{xeCJK}
\usepackage{hyperref}
\usepackage{listings}
\lstset{
 columns=fixed,       
 numbers=left,                                        % 在左侧显示行号
 numberstyle=\tiny\color{gray},                       % 设定行号格式
 frame=single,                                          % 不显示背景边框
 keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
 numberstyle=\footnotesize\color{darkgray},           
 commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
 stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
 showstringspaces=false,                              % 不显示字符串中的空格
 language=c++,                                        % 设置语言
}
\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
\newcommand{\book}[2]{\href[page=#2]{./books/#1.pdf}{(P#2)}}

\title{Log Analysis}
\author{陈辉}
\date{}
\begin{document}
\maketitle
\tableofcontents
\newpage
\section{The Log: What every software engineer should know about real-time data's unifying abstraction}
\href{https://engineering.linkedin.com/distributed-systems/log-what-every-software-engineer-should-know-about-real-time-datas-unifying}{Blog here}
\subsection{What is a log?}
\begin{itemize}
\item Record of ordering activities.
\item Logs in databases: A database uses a log to write out information about the records they will be modifying, before applying the changes to all the various data structures it maintains.
\item Logs in distributed systems:\textbf{State Machine Replication Principle:}

If two identical, deterministic processes begin in the same state and get the same inputs in the same order, they will produce the same output and end in the same state.

\end{itemize}
\end{document}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

### 2018-09-13 FS/presentation.tex
9.13

              
\documentclass{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\title[Your Short Title]{Your Presentation}
\author{You}
\institute{Where You're From}
\date{Date of Presentation}

@@

% Uncomment these lines for an automatically generated outline.
%\begin{frame}{Outline}
%  \tableofcontents
%\end{frame}

\section{Introduction}

\begin{frame}{Introduction}

\begin{itemize}
  \item Your introduction goes here!
  \item Use \texttt{itemize} to organize your main points.
\end{itemize}

\vskip 1cm

\begin{block}{Examples}
Some examples of commonly used commands and features are included, to help you get started.
\end{block}

@@

\section{Some \LaTeX{} Examples}

\subsection{Tables and Figures}

\begin{frame}{Tables and Figures}

\begin{itemize}
\item Use \texttt{tabular} for basic tables --- see Table~\ref{tab:widgets}, for example.
\item You can upload a figure (JPEG, PNG or PDF) using the files menu. 
\item To include it in your document, use the \texttt{includegraphics} command (see the comment below in the source code).
\end{itemize}

% Commands to include a figure:
%\begin{figure}
%\includegraphics[width=\textwidth]{your-figure's-file-name}
%\caption{\label{fig:your-figure}Caption goes here.}
%\end{figure}

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{Mathematics}

\begin{frame}{Readable Mathematics}

Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i$$
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

>>>>

              
\documentclass[xelatex]{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
\usepackage{xeCJK}
\usepackage{verbatim}

\title[Your Short Title]{基于GlusterFS的数据分布策略研究}
\author{陈辉}
%\institute{Where You're From}
\date{}

@@

% Uncomment these lines for an automatically generated outline.
\begin{frame}{Outline}
  \tableofcontents
\end{frame}
\section{Introduction}
\begin{frame}{概述}
本研究致力于在分布式（或高性能计算）环境下，针对不同工作负载进行冷热数据动态负载均衡。主要思想是：
\begin{itemize}
\item 对用户程序实时监控，抽取与IO操作相关性较大的行为特征;
\item 根据用户IO读写历史对文件系统中的数据进行聚类;
\item 将用户、用户程序特征与聚类后的数据进行关联;并根据访问时序对聚类后的数据进行粗略排序。
\item 针对正在运行或即将运行的用户程序特征，将关联的数据（主要针对小文件）按时序加载至SSD.
\end{itemize}
\end{frame}

\section{GlusterFS简介}

\begin{frame}{GlusterFS简介}

%\vskip 1cm
\begin{block}{GlusterFS架构简述}
Some examples of commonly used commands and features are included, to help you get started.
\end{block}

\begin{block}{GlusterFS tiering模块}
\end{block}
\end{frame}

\section{数据采集(监控)}
\subsection{日志分析}
\begin{frame}{日志分析}
日志分析能够比较直接地比对分析用户程序运行与系统层IO活动的逻辑关联性.
%此处应有图

@@

\begin{comment}
% Commands to include a figure:
%\begin{figure}
%\includegraphics[width=\textwidth]{your-figure's-file-name}
%\caption{\label{fig:your-figure}Caption goes here.}
%\end{figure}

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{An example table.}
\end{table}
\end{frame}
\end{comment}
